Open Data Quality is Poor but Slowly Improving

### 2021-01-28 outputs/paper/paper.Rmd
tidy references and table

```{r facetedscorestime, fig.cap = "Scores over time", fig.width = 10, fig.height = 5, echo = FALSE, message = FALSE, warning = FALSE}

cleaned_data %>%
  # Create a pivot table so the different types of scores can easily be faceted:
  tidyr::pivot_longer(
    cols = c("quality", "completeness", "freshness", "metadata", "usability", "accessibility"),
                      names_to = "metric",
                      values_to = "scored"
                      ) %>%

@@

  # Facet the plot so we can compare across different types of score:
  facet_wrap(~ metric, ncol = 3, labeller = labeller(metric = StrCap))
```

@@

  # Summarise counts and means for each month:
  summarise(scored = n_distinct(package),
            scores = n_distinct(recorded_at),
            mean_quality = mean(quality),
            mean_accessibility = mean(accessibility),
            mean_completeness = mean(completeness),
            mean_freshness = mean(freshness),
            mean_metadata = mean(metadata),
            mean_usability = mean(usability),
  ) %>%

  # Put the results in a table:
  knitr::kable(digits = 3,
               col.names = c("Year and Month", "Number of Unique Packages Scored",
                "Number of Times the Portal was Scored", "Average Quality", "Average Accessibility",
                "Average Completeness", "Average Freshness", "Average Metadata",
                "Average Usability"),
               booktabs = TRUE,
               escape = FALSE,
               caption = "Scoring by month"
  ) %>%

  # Style the table:
  kableExtra::kable_styling(latex_options = "scale_down")
```

@@

  # Manipulate colors, labels, and scales for easier presentation:
  scale_color_gradientn(colors = c('darkturquoise', 'royalblue2', 'magenta3')) +
  labs(color = "Average Quality score \n across all packages",
    x = "Date recorded",
    y = "Number of packages scored",
    title = "Scoring Frequency Increased Over the Beta Testing Period")+ 
  scale_x_datetime( breaks = date_breaks("2 months"),
                    minor_breaks = date_breaks("1 month"),
                    labels = date_format("%b%d'%y",tz="EST"), # Format the x-axis scale to show Mar13'21, for example
                    expand = c(0,0), # spaces out scale labels for legibility
                    limits = as.POSIXct(strptime(c("2019-12-02 00:00", "2021-01-25 00:00"), # set x-axis limits
                    format = "%Y-%m-%d %H:%M"))) +
  theme_light()
```

>>>>

```{r facetedscorestime, fig.cap = "Scores over time", fig.width = 10, fig.height = 5, echo = FALSE, message = FALSE, warning = FALSE}
cleaned_data %>%
  # Create a pivot table so the different types of scores can easily be faceted:
  tidyr::pivot_longer(
    cols = c("quality", "completeness", "freshness", "metadata", "usability", "accessibility"),
                      names_to = "metric",
                      values_to = "scored"
                      ) %>%

@@

  # Facet the plot so we can compare across different types of score:
  facet_wrap(~ metric, ncol = 3, labeller = labeller(metric = StrCap))

@@

  # Summarise counts and means for each month:
  summarise(scored = n_distinct(package),
            scores = n_distinct(recorded_at),
            mean_accessibility = mean(accessibility),
            mean_completeness = mean(completeness),
            mean_freshness = mean(freshness),
            mean_metadata = mean(metadata),
            mean_usability = mean(usability),
            mean_quality = mean(quality)
  ) %>%

  # Put the results in a table:
  knitr::kable(digits = 3,
               col.names = c("Year and Month", "Unique Packages Scored",
                "Times the Portal was Scored", "Accessibility",
                "Completeness", "Freshness", "Metadata",
                "Usability", "Quality"),
               booktabs = TRUE,
               escape = FALSE,
               caption = "Scoring by month"
  ) %>%

  # Style the table:
  add_header_above(c("", "Counts" = 2, "Average Scores" = 6)) %>%
  column_spec(1, width = "5em") %>%
  column_spec(2, width = "5em") %>%
  column_spec(3, width = "5em") %>%
  column_spec(4, width = "5em") %>%
  column_spec(5, width = "5em") %>%
  column_spec(6, width = "5em") %>%
  column_spec(7, width = "5em") %>%
  column_spec(8, width = "5em") %>%
  column_spec(9, width = "5em") %>%
  kableExtra::kable_styling(latex_options = "scale_down")
```

@@

  # Manipulate colors, labels, and scales for easier presentation:
  scale_color_gradientn(colors = c('darkturquoise', 'royalblue2', 'magenta3')) +
  labs(color = "Average \nQuality \nscore \nacross all \npackages",
    x = "Date recorded",
    y = "Number of packages scored",
    title = "Scoring Frequency Increased Over the Beta Testing Period")+ 
  scale_x_datetime( breaks = date_breaks("2 months"),
                    minor_breaks = date_breaks("1 month"),
                    labels = date_format("%b%d'%y",tz="EST"), # Format the x-axis scale to show Mar13'21, for example
                    expand = c(0,0), # spaces out scale labels for legibility
                    limits = as.POSIXct(strptime(c("2019-12-16 00:00", "2021-01-25 00:00"), # set x-axis limits
                    format = "%Y-%m-%d %H:%M"))) +
  theme_light()
```
